Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-01-27 text/src/article.tex
Revise second section of implementation

The specification of the nucleotide sequences comprising the genome scaffold is
written using YAML \cite{yaml}. YAML is a data format using whitespace and
identation to produce a standardised machine readable structure. As a commonly
accepted data format third-party developers have the option to generate
a genome scaffold using their programming language of choice. As a standardised
format YAML formatted scaffold files can checked for syntax validity using
third party tools such as Kwalify\cite{kwalify}. \pb

In addition to being machine readable it also important that a genome scaffold
file also be easy to edit manually. As such this was the second reason the YAML
syntax was selected for the scaffold file data format. YAML has a concise and
compact syntax and when compared with formats such as extensible markup
language (XML) which require angular braces (`$<$' and `$>$') and open and
closing tags to delimite each data field.

By choosing a human readable syntax it is aimed that the scaffold should be
easier to edit and change manually in simple text edit.  A scenario which we
anticipate is common in the on-going process of scaffolding a genome sequence.
\pb

The entries in the YAML scaffold are defined as a list. Each entry in the list
corresponds to a region sequence in the final output sequence which follows the
previous entry in the scaffold and precedes the following entry.  Each
attribute defined for each entry in the list allows specifications for the
entry such as if any starting sequence should be clipped from the beginning or
end, or if the sequence should be reversed. \pb

>>>>

The choice of nucleotide sequences comprising the genome scaffold is specified
in YAML \cite{yaml}. YAML is a language format for data using whitespace and
identation to produce a machine readable structure. As a standardised data
format third-party developers have the option to generate a genome scaffold
using any programming language for which a YAML parser exists. Furthermore YAML
formatted scaffold files can be validated using third party tools such as
Kwalify\cite{kwalify}.\pb

The initial assembly of sequencing reads may result in an incomplete genome
build. Comparison of contigs to reference genomes and the generation of
additional sequence from PCR translates to genome finishing as an ongoing
process. Therefore the scaffold file should be simple to edit manually in
additon to being computationally tractable. This requirement for the scaffold
files to be modifable in a simple simple text editor is the second reason YAML
was selected as the format for scaffold files.\pb

The entries in the YAML scaffold are defined as a list. Each entry in the list
corresponds to a region sequence in the final output sequence which follows the
previous entry in the scaffold and precedes the following entry.  Each
attribute defined for each entry in the list allows specifications for the
entry such as if any starting sequence should be clipped from the beginning or
end, or if the sequence should be reversed.\pb
